### 2021-10-06 submission/manuscript.tex
Add running title

@@

\textbf{Reproducibility.} All analyses were performed using mothur
(version 1.44.1) and R (version 4.0.2) with the tidyverse (version
1.3.0), broom (version 0.7.0), data.table (version 1.13.4), and cowplot
(version 1.1.0) packages. All of the code that was used in this analysis
as well as the Makefile for running the analysis are available at
\url{https://github.com/SchlossLab/Schloss_Singletons_XXXXX_2019} along
with the complete version history of the project.

>>>>

\vspace{10mm}

\textbf{Running title:} Removal of rare ASVs biases community analyses

\vspace{25mm}

@@

\textbf{Reproducibility.} All analyses were performed using mothur
(version 1.44.1) and R (version 4.0.3) with the tidyverse (version
1.3.1), broom (version 0.7.8), data.table (version 1.13.4), and cowplot
(version 1.1.0) packages. All of the code that was used in this analysis
as well as the Makefile for running the analysis are available at
\url{https://github.com/SchlossLab/Schloss_Singletons_XXXXX_2019} along
with the complete version history of the project.
